Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-09-22 papers/paper_arxiv_v2/ms.tex
AJ: accepted
Update arxiv upload

%\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
%\documentclass[12pt,twocolumn]{aastex63}
%\documentclass[12pt,modern,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{2022 May 2}
\revised{2022 Sep 14}
\accepted{---}
%\submitjournal{AAS Journals}
\shorttitle{Kepler and the Behemoth}

@@

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar groups
\citep[{e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.
\replaced{To date these analyses have mostly clustered on stellar
positions and 2D velocities}{So far, these analyses have mostly
leveraged 3D stellar positions and 2D on-sky tangential velocities}.
One important result has been the discovery of diffuse
streams and tidal tails comparable in stellar mass to the previously
known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  Even
though these streams are spread over tens to hundreds of parsecs,
their velocity dispersions can remain coherent at the $\sim$1\kms\
level.  Internal dynamics and projection effects can also drive them
to be much \replaced{larger}{more kinematically diffuse}: in the Hyades, stars in the tidal tails are
expected to span up to $\pm 40\mkms$ in velocity relative to the
cluster center \citep{jerabkova_800_2021}.  The stars in such diffuse
regions can be verified to be the same age as the core cluster members
through analyses of color--absolute magnitude diagrams
\citep{KounkelCovey2019}, stellar rotation periods
\citep{curtis_tess_2019,bouma_2021_ngc2516}, and chemical abundances
\citep{hawkins_2020,2020A&A...635L..13A}.  While there are implications for our
understanding of star formation and cluster evolution
\citep{dinnbier_tidal_2020}, a separate consequence is that we now
know the ages of many more stars, including previously known planet
hosts.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.  Kepler-1627 is in the outskirts of the $\delta$\ Lyr
  cluster \citep{bouma_kep1627_2022}, which is centered at $(l,b)
  \approx (66^\circ, 12^\circ)$.
  The Kepler footprint is shown in gray.
  {\it Middle row}: Galactic positions.  The Sun is at $(X, Y, Z) =
  (0, 0, 20.8)$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest \citep{schonrich_local_2010}.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta\added{; smaller circles}).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green\added{; larger
  circles}).
  The selection method for \replaced{all of the stars}{these groups}
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

Our focus is on a region of the Galaxy 200 to 500\,pc
from the Sun, above the galactic plane, and spanning galactic
longitudes of $40^\circ$ to $100^\circ$.  Two rich clusters in
this region are the $\delta$\ Lyr cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Each of these clusters was known before Gaia.  Their reported ages are
between 30 and 60\,Myr.  Early empirical evidence that these two
clusters could be part of a large and more diffuse population was
apparent in the Gaia-based photometric analysis of pre-main-sequence
stars by \citet[][compare their Figures~11 and~13 to our
Figure~\ref{fig:XYZvtang}]{Zari2018}.  Further kinematic connections
and complexity were highlighted by \citet{KounkelCovey2019}, who
included these previously known groups in the larger structures dubbed
``Theia~73'' and ``Theia~96''\footnote{See their visualization online
at \url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March
2022)\added{. Important caveats, particularly for extended groups $\gtrsim 100$\,Myr
old, were presented by \citet{2022arXiv220514160Z}.}}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and on-sky velocities with a subsequent manual ``stitching'' step.
Their results support the idea that there is an overdensity of 30 to
60\,Myr old stars in this region of the Galaxy.  \citet{Kerr2021}, in
a volume-limited analysis of the Gaia DR2 point-source catalog out to
one third of a kiloparsec, identified three of the nearest
sub-populations\added{ of Cep-Her}, dubbed ``Cepheus-Cygnus'', ``Lyra'', and
``Cerberus''.  \citet{Kerr2021} reported ages for each of these
subgroups between 30 and 35 Myr.

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and the
sub-populations identified by \citet{Kerr2021} share a common origin
has yet to be fully substantiated, but preliminary clustering results
from the 1\,kpc SPYGLASS analysis (R.~Kerr et al.\ in prep) suggest
the presence of contiguous stellar populations connecting each of
these groups in \replaced{space-velocity}{both space and velocity} coordinates.  In other words, the stars
appear to be comoving, though with a continuous gradient in velocity
as a function of position\replaced{ (Figure~\ref{fig:XYZvtang}, lower
panels).}{. The lower panels of Figure~\ref{fig:XYZvtang} show this in
detail, where $v_b$ is the distance-corrected proper motion in the
direction of increasing galactic latitude, and $v_{l^*}=v_l \cos b$ is
the distance-corrected proper motion in the direction of increasing
galactic longitude after accounting for the local tangent plane
correction.  Some, but not all, of the gradient in the $v_{l^*}$ vs.~$l$
plane can be understood through a projection effect stemming from the
Sun's motion with respect to the local standard of rest (see also
Figure 11 by \citealt{Zari2018}).  }
In this work, our primary interest in \replaced{the region}{this
region of sky} stems
from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore this
sub-population, we select candidate Cep-Her members through four
steps, the first three being identical to those described in Section~3
of \citet{Kerr2021}.  We briefly summarize them here.

@@

The second step is to perform an unsupervised HDBSCAN clustering on
the photometrically selected population
\citep{campello_hierarchical_2015,mcinnes_hdbscan_2017}.  The
parameters we use in the clustering are $\{ X, Y, Z, c v_b, c v_{l^*}
\} $, where $c$ is
the size-velocity corrective factor, which is taken as $c=6\,{\rm pc /
km\,s}^{-1}$ to ensure that the spatial and velocity scales have
identical standard deviations.  Positions are computed assuming the
\texttt{astropy v4.0} coordinate standard
\citep{astropy_2018}. %, which places the Sun $8122$ pc from the galactic
%center, and assumes the solar velocity with respect to the local
%standard of rest from \citet{schonrich_local_2010}.  
As input
parameters to HDBSCAN, we set the minimum $\epsilon$ threshold past
which clusters cannot be fragmented as $25$\,pc in physical space, and
$25/c$\,\kms\ in velocity.  The minimum cluster size $N$ is set to 10, as
is $k$, the parameter used to define the ``core distance'' density
metric. 
\added{Core distance is the distance to the $k^{\rm th}$ nearest star,
and therefore $k$ acts as a smoothing parameter, where a larger value
reduces the influence of local overdensities smaller than the
scale that interests us.}

The unsupervised clustering in this case yielded 8 distinct subgroups.
These groups are then used as the ``seed'' populations\replaced{ for
the third step, which is to search for objects at least as close to
the 10$^{\rm th}$ nearest HDBSCAN-identified member in space-velocity
coordinates}{, in which the stellar members each have their own
individually-assigned distances to their tenth-nearest
photometrically-young neighbor.  Using those distances, we search the
entire Gaia EDR3 point source catalog for stars that fall within each
star's 10$^{\rm th}$ nearest-neighbor distance}.  This third step yields
stars that are spatially and kinematically close to the
photometrically young stars, but which cannot be identified as young
based on their positions in the color--absolute magnitude diagram.

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$D$, defined such that the group member with the smallest core
distance has $D=1$, the group member with the greatest core
distance has $D=0$, and \replaced{weights for the other group members are
log-normally distributed between these two extremes}{the weight $D$
scales linearly between the two extremes}.  After applying a
set of quality cuts on the astrometry and
photometry\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$}
this procedure yields \replaced{$D \sim \log_{10}\mathcal{N}(-1.55,0.61)$}{a distribution of weights $D$
that is well described by a log-normal distribution with
$\log_{10}\mathcal{N}(-1.55,0.61)$}.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $D>0.02$ as gray points, and 
4{,}763 objects with $D>0.10$ as black points.  \added{These thresholds were
selected visually based on the apparent purity with which they yielded
pre-main-sequence stars on a color--absolute magnitude diagram.} The
$\delta$~Lyr\ cluster is visible at $(l,b)=(68^\circ,15^\circ$) and $(v_{l^*},
v_b)=(-4.5 ,-4 )\mkms$.  RSG-5 is visible at $(l,b)=(83^\circ,6^\circ)$,
$(v_{l^*}, v_b)=(5.5 ,-3.5 )\mkms$.  Most of the other subclusters, including
in Cep-Cyg ($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great detail.

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members with
weights exceeding 0.02, this yielded 11 known false positives, 6
confirmed planets, and 8 candidate planets (see Appendix~\ref{app:members}).
To determine whether these objects were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, we inspected the Kepler data validation
reports and Robovetter classifications.  Youth was assessed based on
the presence of rotational modulation at the expected period and
amplitude \added{for stars at least as young as the Pleiades} \citep[{e.g.},][]{rebull_rotation_2020}. 
Planetary status was assessed through the Robovetter flags, and by
requiring non-grazing transits with ${\rm S/N}>10$.
Four objects passed both cuts: Kepler-1627, Kepler-1643, KOI-7368, and
KOI-7913.
% FIXME: if you need to add lines, "One object (Kepler-1933) was ambiguous,

@@

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members near Kepler-1643, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 80] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -2.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [3.5, 6], \nonumber
\end{align}
though RSG-5 does have a greater spatial extent toward smaller
$X$ (Figure~\ref{fig:XYZvtang}, middle panels).  For the diffuse stars
near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
\end{align}
and we call this latter set of stars ``CH-2'', using the preliminary 
Cep-Her (CH) subgroup identifier from R.~Kerr et al.\ (in prep).
These cuts yielded
\nrsgfive\ candidate RSG-5 members, and \nchtwo\ candidate CH-2
members.  These stars are listed in Appendix~\ref{app:members}, \replaced{as are
the Cep-Her candidates that were observed by Kepler}{as is the set of Cep-Her
candidates that was observed by Kepler}.
%An important
%consideration, especially for CH-2, is the contamination rate by field
%stars.  We assess this in the following section.

@@

		\vspace{-0cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Age-diagnostic diagrams from the stellar groups near
    Kepler-1643, KOI-7368, and KOI-7913.} 
    {\it Top row}: Color--absolute magnitude diagram of candidate
    Cep-Her members, plotted over candidate members of the
    $\delta$~Lyr~cluster ($\approx38$\,Myr;
    \citealt{bouma_kep1627_2022}) and the Gaia EDR3 Catalog of Nearby
    Stars (gray background).  The left and right columns shows stars
    in RSG-5 and CH-2, respectively.  The range of colors is truncated
    to emphasize the pre-main-sequence\added{; approximate spectral types are shown on the upper axes}.  Stars that fall far below the
    cluster sequences are field interlopers.  {\it Bottom row}:
    TESS and ZTF-derived stellar rotation periods, with the Pleiades
    ($\approx 112$\,Myr) and Praesepe ($\approx 650$\,Myr) shown for
    reference \citep{rebull_rotation_2016a,douglas_poking_2017}.  The
    detection efficiency for reliable rotation periods falls off
    beyond $\bpmrpo \gtrsim 2.6$.
	\label{fig:age}
	}
\end{figure*}

@@

Color--absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet[][Appendix~B]{GaiaCollaboration2018}, which include binaries
while omitting artifacts from for instance low
photometric signal to noise, or a small number of visibility periods.
We then corrected for extinction using the
\citet{lallement_threedimensional_2018} dust
maps and the extinction
coefficients $k_X\equiv A_X/A_0$ from \citet{GaiaCollaboration2018},
assuming that $A_0 = 3.1 E(B-V)$.  This yielded a mean and standard
deviation for the reddening of $E(B-V)=0.036\pm0.002$ for RSG-5, and
$E(B-V)=0.017\pm0.001$ for CH-2.  By way of comparison, in
\citet{bouma_kep1627_2022} the same query for the $\delta$~Lyr cluster
yielded $E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the
color \replaced{range}{axis} to best visualize the region of maximal age information
content: the pre-main-sequence.

The CAMDs show that for RSG-5, all but one of the candidate
members are on a tight pre-main-sequence locus.  \added{Quantitatively,
88/89 stars with $\bpmrpo \geq 1.5$ are consistent with being on the
pre-main-sequence.} This implies a false
positive rate of a few percent, at most.  In comparison, our
\replaced{control}{reference}
sample (the $\delta$~Lyr candidates) has a false positive rate of
$\approx$12\%, based on the number of stars that photometrically
overlap with the field population\deleted{, while being outliers from the bulk
cluster population}.  For CH-2, our membership selection gives 27
objects in the color range displayed, and 23 of them appear to be
consistent with being on the pre-main-sequence.  This
\replaced{implies}{would imply} a false
positive rate in CH-2 of $\approx$15\%.

>>>>

%\documentclass[12pt,modern,twocolumn,tighten]{aastex63}
%\documentclass[12pt,twocolumn]{aastex63}
%\documentclass[12pt,modern,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
\documentclass[12pt,twocolumn,tighten]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{2022 May 2}
\revised{2022 Sep 14}
\accepted{2022 Sep 17}
\submitjournal{Astronomical Journal}
\shorttitle{Kepler and the Behemoth}

@@

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar groups
\citep[{e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.
So far, these analyses have mostly
leveraged 3D stellar positions and 2D on-sky tangential velocities.
One important result has been the discovery of diffuse
streams and tidal tails comparable in stellar mass to the previously
known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  Even
though these streams are spread over tens to hundreds of parsecs,
their velocity dispersions can remain coherent at the $\sim$1\kms\
level.  Internal dynamics and projection effects can also drive them
to be much more kinematically diffuse: in the Hyades, stars in the tidal tails are
expected to span up to $\pm 40\mkms$ in velocity relative to the
cluster center \citep{jerabkova_800_2021}.  The stars in such diffuse
regions can be verified to be the same age as the core cluster members
through analyses of color--absolute magnitude diagrams
\citep{KounkelCovey2019}, stellar rotation periods
\citep{curtis_tess_2019,bouma_2021_ngc2516}, and chemical abundances
\citep{hawkins_2020,2020A&A...635L..13A}.  While there are implications for our
understanding of star formation and cluster evolution
\citep{dinnbier_tidal_2020}, a separate consequence is that we now
know the ages of many more stars, including previously known planet
hosts.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.  Kepler-1627 is in the outskirts of the $\delta$\ Lyr
  cluster \citep{bouma_kep1627_2022}, which is centered at $(l,b)
  \approx (66^\circ, 12^\circ)$.
  The Kepler footprint is shown in gray.
  {\it Middle row}: Galactic positions.  The Sun is at $(X, Y, Z) =
  (0, 0, 20.8)$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest \citep{schonrich_local_2010}.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta; smaller circles).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green; larger
  circles).
  The selection method for these groups
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

Our focus is on a region of the Galaxy 200 to 500\,pc
from the Sun, above the galactic plane, and spanning galactic
longitudes of $40^\circ$ to $100^\circ$.  Two rich clusters in
this region are the $\delta$\ Lyr cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Each of these clusters was known before Gaia.  Their reported ages are
between 30 and 60\,Myr.  Early empirical evidence that these two
clusters could be part of a large and more diffuse population was
apparent in the Gaia-based photometric analysis of pre-main-sequence
stars by \citet[][compare their Figures~11 and~13 to our
Figure~\ref{fig:XYZvtang}]{Zari2018}.  Further kinematic connections
and complexity were highlighted by \citet{KounkelCovey2019}, who
included these previously known groups in the larger structures dubbed
``Theia~73'' and ``Theia~96''\footnote{See their visualization online
at \url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March
2022). Important caveats, particularly for extended groups $\gtrsim 100$\,Myr
old, were presented by \citet{2022arXiv220514160Z}.}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and on-sky velocities with a subsequent manual ``stitching'' step.
Their results support the idea that there is an overdensity of 30 to
60\,Myr old stars in this region of the Galaxy.  \citet{Kerr2021}, in
a volume-limited analysis of the Gaia DR2 point-source catalog out to
one third of a kiloparsec, identified three of the nearest
sub-populations of Cep-Her, dubbed ``Cepheus-Cygnus'', ``Lyra'', and
``Cerberus''.  \citet{Kerr2021} reported ages for each of these
subgroups between 30 and 35 Myr.

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and the
sub-populations identified by \citet{Kerr2021} share a common origin
has yet to be fully substantiated, but preliminary clustering results
from the 1\,kpc SPYGLASS analysis (R.~Kerr et al.\ in prep) suggest
the presence of contiguous stellar populations connecting each of
these groups in both space and velocity coordinates.  In other words, the stars
appear to be comoving, though with a continuous gradient in velocity
as a function of position. The lower panels of Figure~\ref{fig:XYZvtang} show this in
detail, where $v_b$ is the distance-corrected proper motion in the
direction of increasing galactic latitude, and $v_{l^*}=v_l \cos b$ is
the distance-corrected proper motion in the direction of increasing
galactic longitude after accounting for the local tangent plane
correction.  Some, but not all, of the gradient in the $v_{l^*}$ vs.~$l$
plane can be understood through a projection effect stemming from the
Sun's motion with respect to the local standard of rest (see also
Figure 11 by \citealt{Zari2018}).  
In this work, our primary interest in this
region of sky stems
from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore this
sub-population, we select candidate Cep-Her members through four
steps, the first three being identical to those described in Section~3
of \citet{Kerr2021}.  We briefly summarize them here.

@@

The second step is to perform an unsupervised HDBSCAN clustering on
the photometrically selected population
\citep{campello_hierarchical_2015,mcinnes_hdbscan_2017}.  The
parameters we use in the clustering are $\{ X, Y, Z, c v_b, c v_{l^*}
\} $, where $c$ is
the size-velocity corrective factor, which is taken as $c=6\,{\rm pc /
km\,s}^{-1}$ to ensure that the spatial and velocity scales have
identical standard deviations.  Positions are computed assuming the
\texttt{astropy v4.0} coordinate standard
\citep{astropy_2018}. %, which places the Sun $8122$ pc from the galactic
%center, and assumes the solar velocity with respect to the local
%standard of rest from \citet{schonrich_local_2010}.  
As input
parameters to HDBSCAN, we set the minimum $\epsilon$ threshold past
which clusters cannot be fragmented as $25$\,pc in physical space, and
$25/c$\,\kms\ in velocity.  The minimum cluster size $N$ is set to 10, as
is $k$, the parameter used to define the ``core distance'' density
metric. 
Core distance is the distance to the $k^{\rm th}$ nearest star,
and therefore $k$ acts as a smoothing parameter, where a larger value
reduces the influence of local overdensities smaller than the
scale that interests us.

The unsupervised clustering in this case yielded 8 distinct subgroups.
These groups are then used as the ``seed'' populations, in which the stellar members each have their own
individually-assigned distances to their tenth-nearest
photometrically-young neighbor.  Using those distances, we search the
entire Gaia EDR3 point source catalog for stars that fall within each
star's 10$^{\rm th}$ nearest-neighbor distance.  This third step yields
stars that are spatially and kinematically close to the
photometrically young stars, but which cannot be identified as young
based on their positions in the color--absolute magnitude diagram.

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$D$, defined such that the group member with the smallest core
distance has $D=1$, the group member with the greatest core
distance has $D=0$, and the weight $D$
scales linearly between the two extremes.  After applying a
set of quality cuts on the astrometry and
photometry\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$}
this procedure yields a distribution of weights $D$
that is well described by a log-normal distribution with
$\log_{10}\mathcal{N}(-1.55,0.61)$.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $D>0.02$ as gray points, and 
4{,}763 objects with $D>0.10$ as black points.  These thresholds were
selected visually based on the apparent purity with which they yielded
pre-main-sequence stars on a color--absolute magnitude diagram. The
$\delta$~Lyr\ cluster is visible at $(l,b)=(68^\circ,15^\circ$) and $(v_{l^*},
v_b)=(-4.5 ,-4 )\mkms$.  RSG-5 is visible at $(l,b)=(83^\circ,6^\circ)$,
$(v_{l^*}, v_b)=(5.5 ,-3.5 )\mkms$.  Most of the other subclusters, including
in Cep-Cyg ($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great detail.

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members with
weights exceeding 0.02, this yielded 11 known false positives, 6
confirmed planets, and 8 candidate planets (see Appendix~\ref{app:members}).
To determine whether these objects were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, we inspected the Kepler data validation
reports and Robovetter classifications.  Youth was assessed based on
the presence of rotational modulation at the expected period and
amplitude for stars at least as young as the Pleiades \citep[{e.g.},][]{rebull_rotation_2020}. 
Planetary status was assessed through the Robovetter flags, and by
requiring non-grazing transits with ${\rm S/N}>10$.
Four objects passed both cuts: Kepler-1627, Kepler-1643, KOI-7368, and
KOI-7913.
% FIXME: if you need to add lines, "One object (Kepler-1933) was ambiguous,

@@

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members near Kepler-1643, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 80] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -2.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [3.5, 6], \nonumber
\end{align}
though RSG-5 does have a greater spatial extent toward smaller
$X$ (Figure~\ref{fig:XYZvtang}, middle panels).  For the diffuse stars
near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
\end{align}
and we call this latter set of stars ``CH-2'', using the preliminary 
Cep-Her (CH) subgroup identifier from R.~Kerr et al.\ (in prep).
These cuts yielded
\nrsgfive\ candidate RSG-5 members, and \nchtwo\ candidate CH-2
members.  These stars are listed in Appendix~\ref{app:members}, as is the set of Cep-Her
candidates that was observed by Kepler.
%An important
%consideration, especially for CH-2, is the contamination rate by field
%stars.  We assess this in the following section.

@@

		\vspace{-0cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Age-diagnostic diagrams from the stellar groups near
    Kepler-1643, KOI-7368, and KOI-7913.} 
    {\it Top row}: Color--absolute magnitude diagram of candidate
    Cep-Her members, plotted over candidate members of the
    $\delta$~Lyr~cluster ($\approx38$\,Myr;
    \citealt{bouma_kep1627_2022}) and the Gaia EDR3 Catalog of Nearby
    Stars (gray background).  The left and right columns shows stars
    in RSG-5 and CH-2, respectively.  The range of colors is truncated
    to emphasize the pre-main-sequence; approximate spectral types are shown on the upper axes.  Stars that fall far below the
    cluster sequences are field interlopers.  {\it Bottom row}:
    TESS and ZTF-derived stellar rotation periods, with the Pleiades
    ($\approx 112$\,Myr) and Praesepe ($\approx 650$\,Myr) shown for
    reference \citep{rebull_rotation_2016a,douglas_poking_2017}.  The
    detection efficiency for reliable rotation periods falls off
    beyond $\bpmrpo \gtrsim 2.6$.
	\label{fig:age}
	}
\end{figure*}

@@

Color--absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet[][Appendix~B]{GaiaCollaboration2018}, which include binaries
while omitting artifacts from for instance low
photometric signal to noise, or a small number of visibility periods.
We then corrected for extinction using the
\citet{lallement_threedimensional_2018} dust
maps and the extinction
coefficients $k_X\equiv A_X/A_0$ from \citet{GaiaCollaboration2018},
assuming that $A_0 = 3.1 E(B-V)$.  This yielded a mean and standard
deviation for the reddening of $E(B-V)=0.036\pm0.002$ for RSG-5, and
$E(B-V)=0.017\pm0.001$ for CH-2.  By way of comparison, in
\citet{bouma_kep1627_2022} the same query for the $\delta$~Lyr cluster
yielded $E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the
color axis to best visualize the region of maximal age information
content: the pre-main-sequence.

The CAMDs show that for RSG-5, all but one of the candidate
members are on a tight pre-main-sequence locus.  Quantitatively,
88/89 stars with $\bpmrpo \geq 1.5$ are consistent with being on the
pre-main-sequence. This implies a false
positive rate of a few percent, at most.  In comparison, our
reference
sample (the $\delta$~Lyr candidates) has a false positive rate of
$\approx$12\%, based on the number of stars that photometrically
overlap with the field population.  For CH-2, our membership selection gives 27
objects in the color range displayed, and 23 of them appear to be
consistent with being on the pre-main-sequence.  This
would imply a false
positive rate in CH-2 of $\approx$15\%.
